%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% NAME:             projects.tex
%
% AUTHOR:           Ethan D. Twardy
%
% DESCRIPTION:      This is a LaTeX file containing some info about my projects.
%
% CREATED:          10/30/2017
%
% LAST EDITED:      10/30/2017
%%%

\documentclass[10pt]{article}
\usepackage{fancyhdr}
\usepackage[margin=0.75in]{geometry}
\usepackage{tikz}
\usepackage{wrapfig}

% Header
\pagestyle{fancy}
\fancyhf{}
\setlength{\headheight}{24pt}
\rhead{Ethan D. Twardy\\Project Information}
\lhead{October 30, 2017}

\begin{document}
\begin{abstract}
  This document is to serve as a declaration of intention. It outlines many of
  my larger projects, describing their goals, procedures \& workflows, and any
  other relevant information necessary to begin the project. This brief contains
  a simple list of projects, each with a number. That number is the
  corresponding section under which a more detailed description of the project
  can be found. Any entry which begins with the word \emph{(Undocumented)} in
  parentheses is included in the list, but not documented in further detail
  elsewhere in the document. This is usually temporary.

  \begin{enumerate}
  \item \emph{(Undocumented)} \textbf{Adviser} - (No, that's not a spelling
    mistake) Program which builds a schedule for a student.
    \begin{itemize}
    \item Finish implementing the audit-JSON parser
    \item Implement the web-crawling facilities
    \item Implement the schedule building facilities
    \item Consider using a Flask App for delivery.
    \end{itemize}
  \item \emph{(Undocumented)} \textbf{Femtofs} - Develop a micro filesystem
    for use with embedded projects or projects using small external peripheral
    bus memory devices. The goal is for barebones functionality and ease of
    extension.
  \item \emph{(Undocumented)} \textbf{Brew-inator} - An automatic beer brewing
    machine, built from scratch.
    % Parts for computer:
    %
    % Microcontroller:
    %   atmel.com/products/selector_overview.aspx
    %       -> Microcontrollers
    %   Filters:
    %       Pin count       48
    %       CPU             Cortex-M3, Cortex-M4
    %       32kHz RTC       Yes
    %       Temp. Sensor    Yes
    %       USB Interface   Device
    %       Hardware QTouch No
    %   digikey.com/products/en
    %       -> Integrated Circuits (ICs) -> Interface - Controllers
    %   Filters:
    %       Series          SAM4S
    %       Manufacturer    Microchip Technology
    %       Package/Case    48-LQFP
    %       Speed           120 MHz
    %       Core Processor  ARM Cortex-M4
    %       Core Size       32-bit Single Core
    %       Part Status     Active
    %
    % Ethernet Controller:
    %   digikey.com/products/en
    %       -> Integrated Circuits (ICs) -> Interface - Controllers
    %   Filters:
    %       Interface   SPI
    %       Protocol    Ethernet
    %   (ENC28J60-I/SS-ND)
    %
    % RJ45 Breakout Board - Digikey, 1568-1097-ND
    %
    % SSOP-28 Breakout Board - Digikey, 1568-1096-ND
    %
    % LQFP-48 Breakout Board - Digikey, PA0094-ND
    \begin{itemize}
    \item Develop an impeller pump system, which requires developing a
      homemade brushless DC motor and controller. Create a state diagram for the
      controller (Moore machine?) and design a test circuit for the controller.
      Then design and build the motor. Finally, use the motor to implement an
      impeller pump.
    \end{itemize}
  \item \emph{(Undocumented)} \textbf{Hey, Porter} - Computer system and intranet
    which implements ``smart-home'' technology. ``Hey, Porter'' will be the
    keywords which start the listener, much like ``OK, Google'', or ``Alexa''.
    It is named after the Johnny Cash song.
    \begin{itemize}
    \item Utilize Google's speech-to-text engine, develop a microcontroller
      node which will communicate with the master node via Ethernet. Create a
      voice that has character, for once. Decision trees that affect
      pronunciation?
    \item Cannibalize a commercial PC motherboard, reverse-engineering the BIOS
      chip and replacing the BIOS and operating system with a compatible
      bootloader and custom-built OS or RTOS.
    \end{itemize}
  \item \emph{(Undocumented)} \textbf{Matlab Compiler} - Implement a basic
    MATLAB-target binary compiler, with a standard library written in Fortran \&
    C.
  \end{enumerate}
\end{abstract}

\pagebreak
\section{Adviser}

\textbf{Summary:} Implement a web application which students will sign
into using their Banweb username and password. This application will use the
information contained in the student's degree audit to generate a few potential
schedules, taking the difficulty out of scheduling yourself every semester.

\textbf{Workflow:}
\begin{wrapfigure}{l}{0pt}
  \begin{tikzpicture}
  \end{tikzpicture}
\end{wrapfigure}
% \noindent ...
\end{document}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
