%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% NAME:             numerical-problem.tex
%
% AUTHOR:           Ethan D. Twardy
%
% DESCRIPTION:      This file describes the problem of solving a system of
%                   unknown equations, numerically.
%
% CREATED:          11/14/2017
%
% LAST EDITED:      11/15/2017
%%%

\documentclass[11pt]{article}
\usepackage{amsmath}
\usepackage[colorlinks=true]{hyperref}

\begin{document}
Heyo. I've been thinking about this for a couple of days. I think there must be
a method for something like this, but I lack the background for it. The problem
statement is also poorly formed, so if you can think of a better way to
represent this problem, please don't hesitate to say.

You are given a vector, $C$, such as this: \\

\begin{center}
  \begin{math}
    \begin{bmatrix}
      f(a_1, a_2, a_3) \\
      f(a_4) \\
      f(a_1, a_2, a_3, a_4) \\
      f(a_1, a_4, a_5) \\
    \end{bmatrix}
  \end{math}
\end{center}

The exact nature of the functions is not given. You are given a vector,
$A$, of input parameters. \\
\begin{center}
  \begin{math}
    \begin{bmatrix}
      a_1 \\ a_2 \\ a_3 \\ a_4 \\ a_5
    \end{bmatrix}
  \end{math}
\end{center}

Finally, you are given a vector, $B$, of constraints. \\
\begin{center}
  \begin{math}
    \begin{bmatrix}
      b_1 \\ \vdots \\ b_4
    \end{bmatrix}
  \end{math}
\end{center}
(Each entry in the vector is a linear constraint)

The goal is to tune the vector of input parameters, so that each function in $C$
returns a real number which adheres to the constraints in $B$. Note that it is
entirely likely that for some combinations of $B$ and $C$, there does not exist
a set of parameters which satisfies all constraints.

Does this kind of problem seem at all familiar? Do you know of a method that can
be used to solve this kind of thing? I'm not even sure what to call it. It's
similar to {\color{blue}\href{https://en.wikipedia.org/wiki/Linear_Programming}
  {Linear Programming}}, however I don't know enough about the subject to say
with certainty that's what it is.

% Inputs:
% A = [ f, Vout, Vin, i_out, v_ripple]
% A = [ a_1, a_2, a_3, a_4, a_5 ]

% c_t = f(f, Vout, Vin)
% r_sc = f(i_out)
% l_min = f(Vin, Vout, i_out, f)
% c_o = f(i_out, f, v_ripple)

% f(a_1, a_2, a_3)
% f(a_4)
% f(a_1, a_2, a_3, a_4)
% f(a_1, a_4, a_5)

% Outputs:
% B = [ c_t,    r_sc,   l_min,  c_o ]
% B = [ b_1, b_2, b_3, b_4 ]
\end{document}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
