%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% NAME:             Resume-Style1.tex
%
% AUTHOR:           Ethan D. Twardy <edtwardy@mtu.edu>
%
% DESCRIPTION:      My resume, in LaTex
%
% CREATED:          04/05/2020
%
% LAST EDITED:      04/05/2020
%%%

\documentclass[11pt]{article}
\usepackage[margin=0.5in]{geometry} % Set margins
\usepackage{setspace} % \setlength
\usepackage{enumitem} % \setlist
\usepackage{multicol} % multicols environment
\usepackage{titlesec} % \titleformat and \titlesec functions

% Clear style presets
\pagestyle{empty}

% Change font to sans serif
%% \renewcommand{\familydefault}{\sfdefault}

% Change the fontsize of the section headers
\titleformat*{\section}{\Huge\bfseries}
\titleformat*{\subsection}{\Large\bfseries}

% Change the spacing before and after the section headers
\titlespacing{\section}{0pt}{0pt}{0pt}
\titlespacing{\subsection}{0pt}{12pt}{0pt}

% Remove space between \item(s)
\setlist{nosep}

% Remove paragraph indent
\setlength{\parindent}{0pt}

% Change whitespace before and after multicols environment
% This is 50% of the original values
\setlength{\multicolsep}{1.5pt plus 0pt minus 0pt}

\begin{document}
\section*{Ethan Twardy}
+1 (906) 203-4482\\
edtwardy@mtu.edu
\hfill
305 Armory Place\\
github.com/AmateurECE
\hfill
Sault Ste. Marie, MI 49783

\hrulefill

{
  \titlespacing{\subsection}{0pt}{0pt}{0pt}
  \subsection*{Summary}
  Fifth year student with broad internship experience in  multiple branches of
  Software Development. Has proficiency in German and other foreign languages,
  and has completed professional leadership development.
}

\subsection*{Education}
\textbf{Michigan Technological University}, Houghton, MI\\
Computer Engineering
\hfill
Since Fall 2015, Graduating Spring 2020\\
German Minor

\subsection*{Experience}
\textbf{Software Engineering Intern}
\hfill
Plexus Corp., Neenah, WI\\
Summer 2019\\
Developed software for industrial refrigeration control board using Modern C++
and TouchGFX. Interfaced closely with the customer to consistently deliver
value and exceed expectations.\\
Experiences gained:
\begin{itemize}
\item Became familiar with software development in small teams.
\item Fast on-boarding to an Agile team requiring new development practices and
  familiarization with new APIs.
\item Programming in asynchronous embedded environments.
\end{itemize}

\vspace{12pt}
\textbf{Software Engineering Intern}
\hfill
Plexus Corp., Neenah, WI\\
Summer 2018\\
Performed formal software verification testing on product software. Authored
and executed verification test procedures for experimental features. Worked in
a team to correct discovered defects.\\
Experiences gained:
\begin{itemize}
\item Formally verified IEC 62304 Class C medical software.
\item Observed and contributed to aftermarket service of mature product.
\item Gained experience in a high-velocity Agile Scrum team.
\end{itemize}

\vspace{12pt}
\textbf{Embedded Engineering Co-Op}
\hfill
X-ES Engineering, Madison, WI\\
Summer and Fall of 2017\\
Wrote low-level driver software for an application to sanitize non-volatile
memory devices on company products in secure applications. Contributed changes
to the global open-source bootloader U-Boot.\\
Experiences gained:
\begin{itemize}
\item Wrote drivers for proprietary memory and communication devices in secure
  applications.
\item Quickly learned new languages for scripting and programming.
\item Developed a compiler for custom language extensions.
\end{itemize}

%% \vspace{12pt}
%% \textbf{Civil Engineering Intern}
%% \hfill
%% C2AE Engineering, Lansing, MI\\
%% Summers of 2015 and 2016\\
%% Implemented a map of local storm and wastewater systems.\\
%% Experiences:
%% \begin{itemize}
%% \item Collection, organization, and interpretation of relevant field data.
%% \item Worked closely with local engineers and contractors to coordinate
%%   resources and solve problems.
%% \end{itemize}

\subsection*{Campus Involvement}
\begin{itemize}
\item \textbf{Alpha Phi Omega} (Co-ed collegiate service organization):
  Coordinated over 1,200 man hours of volunteer work as the Service Vice
  President in 2019. Led workshops on leadership and self-organizing teams.
\item \textbf{LeaderShape Institute} (Intensive leadership development
  program): Attended in Winter 2016.
\item \textbf{Wadsworth Hall Student Association}: Served as both President and
  Vice President in 2016-2017 year.
\end{itemize}

\begin{multicols}{3}
  [
    \subsection*{Languages and Proficiencies}
  ]
  \begin{itemize}
    \raggedright
  \item C/C++ (Primary)
  \item Python
  \item Java
  \item Bash
  \item Git \& SVN
  \item Agile Practices
  \item Object-Oriented Design
  \item Network Programming
  \item Android
  \end{itemize}
\end{multicols}
\end{document}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
