%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% NAME:             Resume-Style2.tex
%
% AUTHOR:           Ethan D. Twardy <edtwardy@mtu.edu>
%
% DESCRIPTION:      My resume, in LaTex
%
% CREATED:          04/05/2020
%
% LAST EDITED:      04/05/2020
%%%

\documentclass[11pt]{article}
\usepackage[margin=0.5in]{geometry} % Set margins
\usepackage{setspace} % \setlength
\usepackage{enumitem} % \setlist
\usepackage{multicol} % multicols environment
\usepackage{titlesec} % \titleformat and \titlesec functions

% Clear style presets
\pagestyle{empty}

% Change font to sans serif
%% \renewcommand{\familydefault}{\sfdefault}

% Change the fontsize of the section headers
\titleformat*{\section}{\Huge\bfseries}
\titleformat*{\subsection}{\Large\bfseries}

% Change the spacing before and after the section headers
\titlespacing{\section}{0pt}{0pt}{0pt}
\titlespacing{\subsection}{0pt}{12pt}{0pt}

% Remove space between \item(s)
\setlist{nosep}

% Remove paragraph indent
\setlength{\parindent}{0pt}

% Change whitespace before and after multicols environment
% This is 50% of the original values
\setlength{\multicolsep}{1.5pt plus 0pt minus 0pt}

\begin{document}
\section*{Ethan Twardy}
+1 (906) 203-4482\\
edtwardy@mtu.edu
\hfill
305 Armory Place\\
github.com/AmateurECE
\hfill
Sault Ste. Marie, MI 49783

\hrulefill

{
  \titlespacing{\subsection}{0pt}{0pt}{0pt}
  \subsection*{Summary}
  Fifth year student with broad internship experience in a diverse range of
  fields and in multiple branches of Software Development. Has proficiency in
  foreign language and completed professional leadership development with
  experience in student government and Agile teams.
}

\subsection*{Education}
\textbf{Michigan Technological University}, Houghton, MI\\
Computer Engineering
\hfill
Since Fall 2015, Graduating Spring 2020\\
German Minor

\subsection*{Experience}
\textbf{Software Engineering Intern}
\hfill
Plexus Corp., Neenah, WI\\
Summer 2019\\
Developed software for industrial refrigeration control board using Modern C++
and TouchGFX. Interfaced closely with the customer to consistently deliver
value. Used previous experience in Object Oriented Design to develop flexible
and maintainable source. Quickly became familiar with new tools and APIs.

\vspace{12pt}
\textbf{Software Engineering Intern}
\hfill
Plexus Corp., Neenah, WI\\
Summer 2018\\
Authored and executed software verification testing for an IEC 62304 Class C
medical device. Contributed to aftermarket service of a successful and mature
product. Became familiar with Agile Scrum operation. Gained experience working
with products under strict regulation.

\vspace{12pt}
\textbf{Embedded Engineering Co-Op}
\hfill
X-ES Engineering, Madison, WI\\
Summer and Fall of 2017\\
Wrote an application to sanitize non-volatile memory devices on company
products in secure applications. Contributed patches to global U-Boot
repository. Quickly learned new scripting languages and developed a compiler
for custom language extensions.

%% \vspace{12pt}
%% \textbf{Civil Engineering Intern}
%% \hfill
%% C2AE Engineering, Lansing, MI\\
%% Summers of 2015 and 2016\\
%% Implemented a map of local storm and wastewater systems. Collected and
%% organized massive amounts of field data. Worked closely with local engineers
%% and contractors to coordinate resources and solve problems.

\subsection*{Campus Involvement}
\begin{itemize}
\item \textbf{Alpha Phi Omega} (Co-ed collegiate service organization):
  Coordinated over 1,200 man hours of volunteer work as the Service Vice
  President in the 2019 calendar year. The program saw tremendous growth under
  my leadership. Led workshops on leadership and working in self-organizing
  teams.
\item \textbf{LeaderShape Institute} (Intensive leadership development
  program): Attended in Winter 2016.
\item \textbf{Wadsworth Hall Student Association}: Served as both President and
  Vice President in 2016-2017 year.
\item \textbf{WMTU} (Campus radio station): Deejay for three semesters.
\end{itemize}

\subsection*{Foreign Languages}
\begin{itemize}
\item \textbf{German} (5 years): Conversationally fluent, capable of reading
  technical documents with relative ease. Experience in conversation with
  native speakers.
\item \textbf{French} (1 year): Quickly learning and on the way to
  conversational fluency.
\end{itemize}

\begin{multicols}{3}
  [
    \subsection*{Technical Proficiencies}
  ]
  \begin{itemize}
    \raggedright
  \item C/C++ (Primary)
  \item Python
  \item Java
  \item Bash
  \item Git \& SVN
  \item Agile Practices
  \item Object-Oriented Design
  \item Network Programming
  \item Android
  \end{itemize}
\end{multicols}
\end{document}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
